\scuba: iterative map-making with the Sub-Millimetre User Reduction Facility

### 2012-09-06 smurf_paper.tex
Explicitly reference the pong paper
Frossie insists on being last author

\author[Edward~L.~Chapin~et~al.]{
  \parbox[t]{\textwidth}{
    Edward~L.~Chapin$^{1,2}$\thanks{E-mail:~echapin@sciops.esa.int,
      Present address: XMM SOC, ESAC, Apartado 78, 28691 Villanueva de
      la Ca\~nada, Madrid, Spain},
    David~S.~Berry$^{2}$,
    Andrew~G.~Gibb$^{1}$,
    Tim~Jenness$^{2}$,
    Douglas~Scott$^{1}$,
    Frossie~Economou$^2$\thanks{Present address: National Optical
      Astronomy Observatory, 950 N.\ Cherry Avenue, Tucson, AZ 85719, USA},
    Remo~P.~J.~Tilanus$^{2,3}$
  }
  \\
  \\
  $^{1}$Dept. of Physics \& Astronomy, University of British Columbia,
  6224 Agricultural Road, Vancouver, B.C. V6T 1Z1, Canada\\
  $^{2}$JointAstronomy Centre, 660 N. A`oh\={o}k\={u} Place, University
  Park, Hilo, Hawaii 96720, USA\\
  $^{3}$Netherlands Organisation for Scientific Research,
  Laan van Nieuw Oost-Indie 300, NL-2509 AC The Hague, The Netherlands}
\begin{document}

@@

In order to reduce the impact of noise on the final maps, it is
essential that an appropriate scan strategy be used. First, it is
clearly advantageous that the astronomical signals appear in the
lowest-noise region of the power spectrum, namely frequencies above
$f_\mathrm{knee}$. This is achieved by scanning the telescope at large
slew rates, which are practically limited to about
600\,arcsec\,s$^{-2}$ for the JCMT in order to have reasonable
turn-around overheads (the amount of time spent changing direction and
speed, over the largest elevation range possible). At this maximum
speed there is a sample every 3.0\,arcsec, or approximately one third
of the 450\,\micron\ diffraction-limited full-width at half-maximum
(FWHM) -- a typical rule-of-thumb for adequately sampling a Gaussian
point spread function (PSF). The scan patterns are designed,
primarily, to mitigate the effects of low-frequency $1/f$ drift. The
simplest scan one might use is a raster ``boustrophedon'' pattern,
i.e., a series of parallel passes across the field. However, such a
scan yields extremely poor performance for structures that are
transverse to the scan direction, since a long time will have elapsed
between each parallel step. In addition, other periodic noise features
may conspire with such a regularly-spaced pattern to produce periodic
structures in the map, or ``scan-synchronous'' noise. Scan strategies
that visit each region of the map on as many different time scales,
and scan angles as possible, offer the best protection against
large-scale noise; such strategies are said to offer good
cross-linking. As a trade-off between truly random scan patterns and
feasibility of implementation taking into consideration both
mechanical and scheduling constraints, \scuba\ presently has two
primary scan modes: PONG, which covers rectangular areas larger than
the array footprint in a closed pattern that ``bounces'' off the edges
at 45\,degree angles (and also usually combined with a rotation
through a number of fixed position angles to create a ``rotating
PONG'' with even better cross-linking); and a ``constant velocity
daisy'' (CV Daisy) for small areas (of order the array footprint), in
which the telescope moves in a circle, whose centre also slowly traces
out a circle. For a more complete description of the \scuba\ observing
modes, see Section~5 in \citet{holland2012}.

>>>>

\author[Edward~L.~Chapin~et~al.]{
  \parbox[t]{\textwidth}{
    Edward~L.~Chapin$^{1,2}$\thanks{E-mail:~echapin@sciops.esa.int,
      Present address: XMM SOC, ESAC, Apartado 78, 28691 Villanueva de
      la Ca\~nada, Madrid, Spain},
    David~S.~Berry$^{2}$,
    Andrew~G.~Gibb$^{1}$,
    Tim~Jenness$^{2}$,
    Douglas~Scott$^{1}$,
    Remo~P.~J.~Tilanus$^{2,3}$,
    Frossie~Economou$^2$\thanks{Present address: National Optical
      Astronomy Observatory, 950 N.\ Cherry Avenue, Tucson, AZ 85719, USA},
  }
  \\
  \\
  $^{1}$Dept. of Physics \& Astronomy, University of British Columbia,
  6224 Agricultural Road, Vancouver, B.C. V6T 1Z1, Canada\\
  $^{2}$JointAstronomy Centre, 660 N. A`oh\={o}k\={u} Place, University
  Park, Hilo, Hawaii 96720, USA\\
  $^{3}$Netherlands Organisation for Scientific Research,
  Laan van Nieuw Oost-Indie 300, NL-2509 AC The Hague, The Netherlands}
\begin{document}

@@

In order to reduce the impact of noise on the final maps, it is
essential that an appropriate scan strategy be used. First, it is
clearly advantageous that the astronomical signals appear in the
lowest-noise region of the power spectrum, namely frequencies above
$f_\mathrm{knee}$. This is achieved by scanning the telescope at large
slew rates, which are practically limited to about
600\,arcsec\,s$^{-2}$ for the JCMT in order to have reasonable
turn-around overheads (the amount of time spent changing direction and
speed, over the largest elevation range possible). At this maximum
speed there is a sample every 3.0\,arcsec, or approximately one third
of the 450\,\micron\ diffraction-limited full-width at half-maximum
(FWHM) -- a typical rule-of-thumb for adequately sampling a Gaussian
point spread function (PSF). The scan patterns are designed,
primarily, to mitigate the effects of low-frequency $1/f$ drift. The
simplest scan one might use is a raster ``boustrophedon'' pattern,
i.e., a series of parallel passes across the field. However, such a
scan yields extremely poor performance for structures that are
transverse to the scan direction, since a long time will have elapsed
between each parallel step. In addition, other periodic noise features
may conspire with such a regularly-spaced pattern to produce periodic
structures in the map, or ``scan-synchronous'' noise. Scan strategies
that visit each region of the map on as many different time scales,
and scan angles as possible, offer the best protection against
large-scale noise; such strategies are said to offer good
cross-linking. As a trade-off between truly random scan patterns and
feasibility of implementation taking into consideration both
mechanical and scheduling constraints, \scuba\ presently has two
primary scan modes: PONG, which covers rectangular areas larger than
the array footprint in a closed pattern that ``bounces'' off the edges
at 45\,degree angles (and also usually combined with a rotation
through a number of fixed position angles to create a ``rotating
PONG'' with even better cross-linking); and a ``constant velocity
daisy'' (CV Daisy) for small areas (of order the array footprint), in
which the telescope moves in a circle, whose centre also slowly traces
out a circle. For a more complete description of the \scuba\ observing
modes, see Section~5 in \citet{holland2012} and also \citet{2010SPIE.7740E..66K}.
